Refinement for open automata

### 2021-06-14 2021-Refinement/report.tex

\section{Introduction}
The open automata model is used to give the semantic of open pNets \cite{2007.10770}.
Open pNets are not petri nets but an intermediate representation used in the VerCors project to perform verification \cite{henrio:01252323}.
Verification is the process of checking that an implementation satisfies a specification.
Open pNets with the open automaton semantics and equivalence relation introduced in previous work \cite{2007.10770} were sucessfully used to model and verify BIP and GCM \cite{qin:01823507, ameurboulifa:01526055}.
However equivalences relations are not always sufficient to perform verification, refinement relations are also used.
For instance an example of open pNet where equivalence is not sufficient was encountered in an article about algorithms fo weak bisimulation on open automata \cite{wang:03126313}.

The contributions of this article are the definition of composition for open automata without having to define open pNets, and the introduciton of several refinement relations for open automata. % TODO: expand

@@

We begin with Section \ref{sec:notations} by giving some notations used throughout this paper.
Then there are several sections dedicated to define all the interesting objects and properties:
In Section \ref{sec:def} we give a clean and up to date definition of open automata.
In Section \ref{sec:comp} we define their composition without requiring the use of open pNets.
In Section \ref{sec:proofelts} we adapt the standard properties related to refinement relation from LTS to open automata.
After that Section \ref{sec:prelref} is dedicated to progressively build a refinement relation.
Section \ref{sec:refinement} introduces and analyses the refinement relation on open automata.
Finally Section \ref{sec:ccl} recapitulates the contribution and present the work left.

>>>>

\section{Introduction}
The open automata model was originally designed to give the semantic of open pNets \cite{2007.10770}.
Open pNets are not petri nets but an intermediate representation used in the VerCors project to perform verification \cite{henrio:01252323}.
 Verification is the process of checking that an implementation satisfies a specification.
\Ludo{verification is more general than that (or you need to refine specification): checking typing or absence of deadlocks belong to verification}
Open pNets with the open automaton semantics and equivalence relation introduced in previous work \cite{2007.10770} were sucessfully used to model and verify some properties of applications based on BIP  and GCM \cite{qin:01823507, ameurboulifa:01526055} \Ludo{cite and expand acronym (x2)}.
However equivalence relations are not always sufficient to perform verification, refinement relations are also used. \Ludo{verification/refinement/equivalence needs to be refined and explained}
For instance a usecase where open pNet where equivalence is not sufficient can be found  in an article about algorithms fo weak bisimulation on open automata \cite{wang:03126313}.

\Ludo{choose: either 1) you do not refer to open pnets below and explain informally open automata here (why are they useful, what makes them different from automata), or 2) you want to refer to pnets in the following and you explain informally pnets, uatomata and the relation}

The contributions of this article are \Ludo{report?} the definition of composition for open automata without having to define open pNets, and the introduction of several refinement relations for open automata. % TODO: expand

@@

\Ludo{RAPPEL: pour ecrire une intro: 1) on ecrit les contribs, 2) on explique avant les termeis techniques pour que le lecteur comprenne les contribs, 3) quand on a quasi fini le reste on ecrit le plan. ON peut commencer 1 et 2 un peu tot meme si il faut rediger le tout assez tard: on peut pas ecrire proprement un article sans avoir en tete les contribs de celui ci}

We begin with Section \ref{sec:notations} by giving some notations used throughout this paper.
Then there are several sections dedicated to define all the interesting objects and properties:
In Section \ref{sec:def} we give a clean and up to date definition of open automata.
In Section \ref{sec:comp} we define their composition without requiring the use of open pNets \Ludo{does this mean that previous definitions were using open pnets? this might be clarified in contributions but when you redo a definition you must highlight why a new definition was necessary}.
In Section \ref{sec:proofelts} we adapt several standard properties that we use in the definition of refinement relation from LTS to open automata.
After that Section \ref{sec:prelref} is dedicated to progressively build a refinement relation and explain the elements of this construction.
Section \ref{sec:refinement} introduces and analyses the refinement relation on open automata.
Finally Section \ref{sec:ccl} recapitulates the contribution and presents the work left.
